Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-07 paper.qmd
address reviewer 4 remark on mission failures and possible future work.
address reviewer 4 comment on `pax`

These aircraft properties are well-known design parameters. 
While there does not exist a single openly available date base for these aircraft parameters, we collected the information from a series of sources and integrated them into a lookup dataset.
The values $W_t$, $H_t$, $L_t$ and $C_{t}$ have been retrieved from [@performance_database;@skybrary;@doc8643]; we used $\varepsilon_t = \qty{500}{m^2}$
and $pax = 7$ for missing entries which usually are due to smaller aircraft not listed in the above sources.

@@

>>>>

These aircraft properties are well-known design parameters. 
While there does not exist a single openly available date base for these aircraft parameters, we collected the information from a series of sources and integrated them into a lookup dataset.
The values $W_t$, $H_t$, $L_t$ and $C_{t}$ have been retrieved from [@performance_database;@skybrary;@doc8643]; we used $\varepsilon_t = \qty{500}{m^2}$
(and $pax = 7$)[^pax] for missing entries which usually are due to smaller aircraft not listed in the above sources.

[^pax]: `pax` values, i.e. number of passengers, will be used for future work on
        casuality risk calculation.

@@

Of practical interest for the application of this work and future extension
is the scenario of mission failure at launch can typically lead to vast airspace
closure and traffic re-routing: The techniques developed would allow to
quantify risk and impact of the planned measures.
